---
title: "Simulation Results (2/13/17)"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Model

# Algorithms

# Simulation Results

## Model 1 (Standard) Correctly specified

```{r}
create_matrix <- function(glatent_res, glatent_sbm_res, hclust_res, sbm_res){
  glatent_mat <- sapply(glatent_res, function(x){apply(x, 1, mean)})
  glatent_sbm_mat <- sapply(glatent_sbm_res, function(x){apply(x, 1, mean)})
  hclust_mat <- sapply(hclust_res, function(x){apply(x, 1, mean)})
  sbm_mat <- sapply(sbm_res, function(x){apply(x, 1, mean)})
  
  glatent_sd <- sapply(glatent_res, function(x){apply(x, 1, sd)})
  glatent_sbm_sd <- sapply(glatent_res, function(x){apply(x, 1, sd)})
  hclust_sd <- sapply(hclust_res, function(x){apply(x, 1, sd)})
  sbm_sd <- sapply(sbm_res, function(x){apply(x, 1, sd)})
  
  name_vec <- c("Max", "Forbenius", "Spectral", "L1", "Graph Edge Distance",
                "Partnership Difference", "Jaccard Difference")
  
  mean_list <- list(glatent_mat, glatent_sbm_mat, hclust_mat, sbm_mat)
  sd_list <- list(glatent_sd, glatent_sbm_sd, hclust_sd, sbm_sd)
  
  list(mean_list = mean_list, sd_list = sd_list, name_vec = name_vec)
}

plot_data <- function(res, i_vec, n_vec){
  par(mfrow = c(1, length(i_vec)), mar = c(5,1.75,4,1))
  
  for(i in i_vec){
    xlim = c(min(n_vec), max(n_vec))
    ylim = c(min(sapply(1:4, function(x){min(res$mean_list[[x]][i,] -
                                                                   res$sd_list[[x]][i,])})),
      max(sapply(1:4, function(x){max(res$mean_list[[x]][i,] + 
                                                            res$sd_list[[x]][i,])})))
  
    plot(NA, xlim = xlim, ylim = ylim, xlab = "n", ylab = "Error",
         main = res$name.vec[i])
    
    for(j in 1:4){
      offset <- rnorm(1)
      arrows(n_vec + offset, res$mean_list[[j]][i,] - res$sd_list[[j]][i,],
             n_vec + offset, res$mean_list[[j]][i,] + res$sd_list[[j]][i,],
             code = 3, angle = 90, length = 0.02, col = j, lty = 2)
    }
  
    for(j in c(4,3,1,2)){
      lines(n_vec, res$mean_list[[j]][i,], col = j, lwd = 4)
    }
  
    legend("topright", c("GLatent", "GLatent Spectral", "Hier.", "SBM"), fill = 1:4)
  }
  
  invisible()
}
```


```{r}
load("../results/results_standard.RData")

res <- create_matrix(glatent_res, glatent_sbm_res, hclust_res, sbm_res)
```

**Estimation of Latent Covariance Matrix**

```{r}
plot_data(res, 1:4, paramMat[,3])
```

**Estimation of the Clusterings**

```{r}
suppressWarnings(plot_data(res, 6:7, paramMat[,3]))
```

## Model 2 (Fragment: many small clusters) Correctly specified

```{r}
load("../results/results_fragment.RData")

res <- create_matrix(glatent_res, glatent_sbm_res, hclust_res, sbm_res)
```

**Estimation of Latent Covariance Matrix**

```{r}
plot_data(res, 1:4, paramMat[,3])
```

**Estimation of the Clusterings**

```{r}
suppressWarnings(plot_data(res, 6:7, paramMat[,3]))
```

## Model 3 (Blockwise: many clusters of different sizes) Correctly specified

```{r}
load("../results/results_blockwise.RData")

res <- create_matrix(glatent_res, glatent_sbm_res, hclust_res, sbm_res)
```

**Estimation of Latent Covariance Matrix**

```{r}
plot_data(res, 1:4, paramMat[,2])
```

**Estimation of the Clusterings**

```{r}
suppressWarnings(plot_data(res, 6:7, paramMat[,2]))
```
